### 2020-01-09 README.Rmd
update readme. multi treatment SL uses my version of SL methods

__Author:__ [David Benkeser](https://www.benkeserstatistics.com/)

@@

`drtmle` is an R package that computes marginal means of an outcome under fixed
levels of a treatment. The package computes targeted minimum loss-based (TMLE)
estimators that are doubly robust, not only with respect to consistency, but
also with respect to asymptotic normality, as discussed in [Benkeser, et al (2017)](https://academic.oup.com/biomet/article-abstract/104/4/863/4554445). This property
facilitates construction of doubly-robust confidence intervals and hypothesis
tests.

@@

&copy; 2016-2017 [David C. Benkeser](http://www.benkeserstatistics.com)

@@

Copyright (c) 2016-2017 David C. Benkeser

>>>>

__Author:__ [David Benkeser](https://www.sph.emory.edu/faculty/profile/#!dbenkes)

@@

`drtmle` is an R package that computes marginal means of an outcome under fixed
levels of a treatment. The package computes targeted minimum loss-based (TMLE)
estimators that are doubly robust, not only with respect to consistency, but
also with respect to asymptotic normality, as discussed in [Benkeser, et al.
(2017)](https://academic.oup.com/biomet/article-abstract/104/4/863/4554445).
This property facilitates construction of doubly-robust confidence intervals and
hypothesis tests.

@@

&copy; 2016-2019 [David C. Benkeser](https://www.sph.emory.edu/faculty/profile/#!dbenkes)

@@

Copyright (c) 2016-2019 David C. Benkeser
